---
title: "PAH oxidation calibration and quantification"
output: html_notebook
---


```{r, message = FALSE, warning = FALSE, eval = FALSE}
#graphs require ggplot2
library(ggplot2)
library(ggrepel)

#Set your working directory where the data .csv file(s) are located
########################################
########   CHANGE DIRECTORY   ###########
########################################
setwd("~/Desktop/GCMS-LMM")


#Load entire (standards, samples, duplicates) data file of run
########################################
########   CHANGE FILENAME   ###########
########################################
mydata <- read.csv("quechers-triplicate-organized_3.csv")

#Load entire (standards, samples, duplicates) data file of run
SampleInfo <- read.csv("SampleInfo_PAH.csv")

```

Convert any negative area values to 0  
Sorry about the lack of elegance... big dumb hairless ape coding
```{r}
###Convert any negative areas to 0 
#Sorry about the lack of elegance... big dumb hairless ape coding
a <- mydata[,8:ncol(mydata)]
b <- mydata[,1:7]
a[a<0] <- 0
mydata <- cbind(b,a)
```

Locate standards within dataframe  
This code keys on "Std" in the standard name. If the standard names change then we'll need to change this code.  It returns the row numbers in which the standards occur, isolates those standards in a dataframe. We also create a samples data frame here that removes all the standards.
```{r}
#Locate standards
std.loc <- grep("Std", as.character(mydata[,2]))
stds <- mydata[std.loc,]
stds.vars <- c("sample", "name", "rundate", "gc.method", 
               "quant.method", "locate", "Nap_area",	"Acy_area",
               "BrN_area", "Ace_area", "Flu_area", "Phe_area","Ant_area", 
               "Fla_area",	"Pyr_area", "Bza_area", "Cry_area", "Bzf_area", 
               "Bzp_area", "Idp_area", "Dba_area", "Bzy_area")
standards.area <- stds[stds.vars]
samples <- mydata[-std.loc,]
```

This code keys on the standard # (i.e. concentration) which should be in the rightmost part of the cell.  The Standard number is then made into its own column.
```{r}
#function to pick the right most character in a string
substrRight <- function(x, n){
  substr(x, nchar(x)-n+1, nchar(x))
}

#right most character in standard sample name is standard number (needed to take TWO right most characters to make it work)
standards.area$sample <- as.character(standards.area$sample)
standards.area$std.no <- substrRight(standards.area$sample, 1)
standards.area$std.no <- trimws(standards.area$std.no, which = c("both"))
standards.area$std.no <- as.factor(standards.area$std.no)

```

Load csv containing standard concentrations, fix formatting, and merge them with our standards file so that we have area values from GCMS and known concentrations that we can now develop our calibration from.
```{r}
#load csv of standard compound concentrations
########################################
##   CHANGE DIRECTORY AND FILENAME   ###
########################################
standards.conc <- read.csv("Standards_PAH_q2.csv", header=TRUE)
standards.conc$std.no <- trimws(standards.conc$std.no, which = c("both"))
standards.conc$std.no <- as.factor(standards.conc$std.no)

#join standard compound concentrations and standard GC results
standards.all <- merge(standards.area,standards.conc,by="std.no")

#join sample information file and samples files
samples.all <- merge(SampleInfo, samples,by="name")
names(samples.all)[names(samples.all) == 'rundate.x'] <- 'rundate'
names(samples.all)[names(samples.all) == 'sample.x'] <- 'sample'
samples.all <- subset(samples.all, select=-c(X,rundate.y,sample.y))
```

```{r}
#Quantification----
#Quantification of internal standards and development of correction factors


tryme=standards.all
tryme2=samples.all


#import a list of molecules that you want to quantify
all.molecules=read.csv("components.csv")

#make it into a vector of characters
all.molecules$component=as.character(all.molecules$component)
all.molecules <- all.molecules[[1]]


for(molecule in all.molecules)
{
  molecule.area=paste0(molecule,"_area")
  molecule.area.sq = paste0(molecule,"_area2")
  molecule.conc = paste0(molecule,"_ngmL")
  molecule.ng = paste0(molecule,"_ng")
  tryme[[molecule.area.sq]]=tryme[[molecule.area]]^2
  regression=paste(molecule,"_nguL ~ ",molecule,"_area + ",molecule,"_area2",sep="")
  polynomial <- lm(data=tryme,as.formula(regression))
  summary(polynomial)
  r2 <- format(summary(polynomial)$r.squared, digits = 3)
  B0 <- summary(polynomial)$coefficients[1,1]
  B1 <- summary(polynomial)$coefficients[2,1]
  B2 <- summary(polynomial)$coefficients[3,1]
  tryme2[[molecule.area.sq]]
  tryme2[[molecule.conc]] <- B0 + B1*tryme2[[molecule.area]] + B2*(tryme2[[molecule.area]]^2)
  tryme2[[molecule.ng]] <- tryme2[[molecule.conc]]*3.333
  
  #plot the samples and standards
  print(ggplot(tryme, aes_string(x = molecule.area, y = molecule.conc)) +
	geom_point(data=tryme2, aes_string(x=paste0(molecule,"_area"), y=paste0(molecule,"_nguL"), size=2))+
	geom_point() +
	xlab(paste0(molecule,"_area"))+
	ylab(paste0(molecule,"std concentration (ng/uL)"))+
	geom_smooth(method=lm, formula=y ~ poly(x, 2, raw=TRUE))+
	theme(legend.position="none"))
  
  #calculate how many ug of PAH should be recovered for 100% recovery 
  tryme2$full.recovery=SampleInfo$SampleMass.mg*SampleInfo$spike/1000
  
  molecule.rec=paste0(molecule,"_rec")
  tryme2[[molecule.rec]]=tryme2[[molecule.ng]]/tryme2[["full.recovery"]]*100
  
}




########################################
#######END PART I'VE WORKED ON #########
########################################


#uncorrected concentration for plotting
samples.all$Nap_nguL <- Nap.B0 + Nap.B1*samples.all$Nap_area 
Nap.B2*samples.all$Nap_area^2
#plot of calibration curve and samples
library(ggplot2)
ggplot(standards.all, aes(x = Nap_area, y = Nap_nguL)) +
	geom_point(data=samples.all, aes(y=Nap_area, x=Nap_nguL, color="red", size=2))+
	geom_point() +
	xlab("Nap area")+
	ylab("Nap std concentration (ng/uL)")+
	annotate("text", x=x, y=y, hjust=-1,vjust=1,label = Nap.r2)+
	geom_smooth(method=lm, formula=y ~ poly(x, 2, raw=TRUE))+
	theme(legend.position="none")
samples.all$Nap.ng <- samples.all$PyridineVol.uL*samples.all$Nap_nguL
samples.all$RecNap.ng <- samples.all$PyridineVol.uL*samples.all$RecNap.nguL
samples.all$Nap.Recovery <- samples.all$Nap.ng/samples.all$RecNap.ng
ggplot(samples.all, aes(x = CuOSeries, y = Nap.Recovery)) +
	geom_point()

#F
#create a column of area squared in order to do an 2nd order polynomial
standards.all$F_area2 <- standards.all$F_area^2
#polynomial lm
F.poly <- lm(data=standards.all, F_nguL ~ F_area + F_area2)
summary(F.poly)
#r-squared and coefficients used in modeling other compounds
F.r2 <- format(summary(F.poly)$r.squared, digits = 3)
F.B0 <- summary(F.poly)$coefficients[1,1]
F.B1 <- summary(F.poly)$coefficients[2,1]
F.B2 <- summary(F.poly)$coefficients[3,1]
#x and y are used in the annotate function below
x = min(standards.all$F_area)
y = max(standards.all$F_nguL)

samples.all<-samples
#uncorrected concentration for plotting
samples.all$F_nguL <- F.B0 + F.B1*samples.all$F_area + F.B2*samples.all$F_area^2
#plot of calibration curve and samples
ggplot(standards.all, aes(x = F_area, y = F_nguL)) +
	geom_point(data=samples.all, aes(x=F_area, y=F_nguL, color="red", size=2))+
	geom_point() +
	xlab("F area")+
	ylab("F std concentration (ng/uL)")+
	annotate("text", x=x, y=y, hjust=-1,vjust=1,label = F.r2)+
	geom_smooth(method=lm, formula=y ~ poly(x, 2, raw=TRUE))+
	theme(legend.position="none")
samples.all$F.ng <- samples.all$PyridineVol.uL*samples.all$F_nguL
samples.all$RecF.ng <- samples.all$PyridineVol.uL*samples.all$RecF.nguL
samples.all$F.Recovery <- samples.all$F.ng/samples.all$RecF.ng
ggplot(samples.all, aes(x = CuOSeries, y = F.Recovery)) +
	geom_point()

samples.all$F.N <- samples.all$F.ng/samples.all$N.ng
ggplot(samples.all, aes(x = CuOSeries, y = F.N)) +
	geom_point()
```

```{r}
#Quantification of Standards----

#N
standards.all$N_area2 <- standards.all$N_area^2
Bd.poly <- lm(data=standards.all, N_nguL ~ N_area + N_area2)
summary(N.poly)
N.r2 <- format(summary(N.poly)$r.squared, digits = 3)
N.B0 <- summary(N.poly)$coefficients[1,1]
N.B1 <- summary(N.poly)$coefficients[2,1]
N.B2 <- summary(N.poly)$coefficients[3,1]
x = min(standards.all$N_area)
y = max(standards.all$N_nguL)

samples.all$N_nguL.uncorr <- N.B0 + N.B1*samples.all$N_area + N.B2*samples.all$N_area^2
ggplot(standards.all, aes(x = N_area, y = N_nguL)) +
	geom_point(data=samples.all, aes(x=N_area, y=N_nguL.uncorr, color="red", size=2))+
	geom_point() +
	xlab("N area")+
	ylab("N std concentration (ng/uL)")+
	annotate("text", x=x, y=y, hjust=-1,vjust=1,label = N.r2)+
	geom_smooth(method=lm, formula=y ~ poly(x, 2, raw=TRUE))+
	theme(legend.position="none")

#Acy
standards.all$Acy_area2 <- standards.all$Acy_area^2
Acy.poly <- lm(data=standards.all, Acy_nguL ~ Acy_area + Acy_area2)
summary(Acy.poly)
Acy.r2 <- format(summary(Acy.poly)$r.squared, digits = 3)
Acy.B0 <- summary(Acy.poly)$coefficients[1,1]
Acy.B1 <- summary(Acy.poly)$coefficients[2,1]
Acy.B2 <- summary(Acy.poly)$coefficients[3,1]
x = min(standards.all$Acy_area)
y = max(standards.all$Acy_nguL)

samples.all$Acy_nguL.uncorr <- Acy.B0 + Acy.B1*samples.all$Acy_area + Acy.B2*samples.all$Acy_area^2
ggplot(standards.all, aes(x = Acy_area, y = Acy_nguL)) +
	geom_point(data=samples.all, aes(x=Acy_area, y=Acy_nguL.uncorr, color="red", size=2))+
	geom_point() +
	xlab("Acy area")+
	ylab("Acy std concentration (ng/uL)")+
	annotate("text", x=x, y=y, hjust=-1,vjust=1,label = Acy.r2)+
	geom_smooth(method=lm, formula=y ~ poly(x, 2, raw=TRUE))+
	theme(legend.position="none")

#X2BrN
standards.all$X2BrN_area2 <- standards.all$X2BrN_area^2
X2BrN.poly <- lm(data=standards.all, X2BrN_nguL ~ X2BrN_area + X2BrN_area2)
summary(X2BrN.poly)
X2BrN.r2 <- format(summary(X2BrN.poly)$r.squared, digits = 3)
X2BrN.B0 <- summary(X2BrN.poly)$coefficients[1,1]
X2BrN.B1 <- summary(X2BrN.poly)$coefficients[2,1]
X2BrN.B2 <- summary(X2BrN.poly)$coefficients[3,1]
x = min(standards.all$X2BrN_area)
y = max(standards.all$X2BrN_nguL)

samples.all$X2BrN_nguL.uncorr <- X2BrN.B0 + X2BrN.B1*samples.all$X2BrN_area + X2BrN.B2*samples.all$X2BrN_area^2
ggplot(standards.all, aes(x = X2BrN_area, y = X2BrN_nguL)) +
	geom_point(data=samples.all, aes(x=X2BrN_area, y=X2BrN_nguL.uncorr, color="red", size=2))+
	geom_point() +
	xlab("X2BrN area")+
	ylab("X2BrN std concentration (ng/uL)")+
	annotate("text", x=x, y=y, hjust=-1,vjust=1,label = X2BrN.r2)+
	geom_smooth(method=lm, formula=y ~ poly(x, 2, raw=TRUE))+
	theme(legend.position="none")

#Ace
standards.all$Ace_area2 <- standards.all$Ace_area^2
Ace.poly <- lm(data=standards.all, Ace_nguL ~ Ace_area + Ace_area2)
summary(Ace.poly)
Ace.r2 <- format(summary(Ace.poly)$r.squared, digits = 3)
Ace.B0 <- summary(Ace.poly)$coefficients[1,1]
Ace.B1 <- summary(Ace.poly)$coefficients[2,1]
Ace.B2 <- summary(Ace.poly)$coefficients[3,1]
x = min(standards.all$Ace_area)
y = max(standards.all$Ace_nguL)

samples.all$Ace_nguL.uncorr <- Ace.B0 + Ace.B1*samples.all$Ace_area + Ace.B2*samples.all$Ace_area^2
ggplot(standards.all, aes(x = Ace_area, y = Ace_nguL)) +
	geom_point(data=samples.all, aes(x=Ace_area, y=Ace_nguL.uncorr, color="red", size=2))+
	geom_point() +
	xlab("Ace area")+
	ylab("Ace std concentration (ng/uL)")+
	annotate("text", x=x, y=y, hjust=-1,vjust=1,label = Ace.r2)+
	geom_smooth(method=lm, formula=y ~ poly(x, 2, raw=TRUE))+
	theme(legend.position="none")

#F
standards.all$F_area2 <- standards.all$F_area^2
F.poly <- lm(data=standards.all, F_nguL ~ F_area + F_area2)
summary(F.poly)
F.r2 <- format(summary(F.poly)$r.squared, digits = 3)
F.B0 <- summary(F.poly)$coefficients[1,1]
F.B1 <- summary(F.poly)$coefficients[2,1]
F.B2 <- summary(F.poly)$coefficients[3,1]
x = min(standards.all$F_area)
y = max(standards.all$F_nguL)

samples.all$F_nguL.uncorr <- F.B0 + F.B1*samples.all$F_area + F.B2*samples.all$F_area^2
ggplot(standards.all, aes(x = F_area, y = F_nguL)) +
	geom_point(data=samples.all, aes(x=F_area, y=F_nguL.uncorr, color="red", size=2))+
	geom_point() +
	xlab("F area")+
	ylab("F std concentration (ng/uL)")+
	annotate("text", x=x, y=y, hjust=-1,vjust=1,label = F.r2)+
	geom_smooth(method=lm, formula=y ~ poly(x, 2, raw=TRUE))+
	theme(legend.position="none")

#P
standards.all$P_area2 <- standards.all$P_area^2
P.poly <- lm(data=standards.all, P_nguL ~ P_area + P_area2)
summary(P.poly)
P.r2 <- format(summary(P.poly)$r.squared, digits = 3)
P.B0 <- summary(P.poly)$coefficients[1,1]
P.B1 <- summary(P.poly)$coefficients[2,1]
P.B2 <- summary(P.poly)$coefficients[3,1]
x = min(standards.all$P_area)
y = max(standards.all$P_nguL)

samples.all$P_nguL.uncorr <- P.B0 + P.B1*samples.all$P_area + P.B2*samples.all$P_area^2
ggplot(standards.all, aes(x = P_area, y = P_nguL)) +
	geom_point(data=samples.all, aes(x=P_area, y=P_nguL.uncorr, color="red", size=2))+
	geom_point() +
	xlab("P area")+
	ylab("P std concentration (ng/uL)")+
	annotate("text", x=x, y=y, hjust=-1,vjust=1,label = P.r2)+
	geom_smooth(method=lm, formula=y ~ poly(x, 2, raw=TRUE))+
	theme(legend.position="none")



#Ant
standards.all$Ant_area2 <- standards.all$Ant_area^2
Ant.poly <- lm(data=standards.all, Ant_nguL ~ Ant_area + Ant_area2)
summary(Ant.poly)
Ant.r2 <- format(summary(Ant.poly)$r.squared, digits = 3)
Ant.B0 <- summary(Ant.poly)$coefficients[1,1]
Ant.B1 <- summary(Ant.poly)$coefficients[2,1]
Ant.B2 <- summary(Ant.poly)$coefficients[3,1]
x = min(standards.all$Ant_area)
y = max(standards.all$Ant_nguL)

samples.all$Ant_nguL.uncorr <- Ant.B0 + Ant.B1*samples.all$Ant_area + Ant.B2*samples.all$Ant_area^2
ggplot(standards.all, aes(x = Ant_area, y = Ant_nguL)) +
	geom_point(data=samples.all, aes(x=Ant_area, y=Ant_nguL.uncorr, color="red", size=2))+
	geom_point() +
	xlab("Ant area")+
	ylab("Ant std concentration (ng/uL)")+
	annotate("text", x=x, y=y, hjust=-1,vjust=1,label = Ant.r2)+
	geom_smooth(method=lm, formula=y ~ poly(x, 2, raw=TRUE))+
	theme(legend.position="none")

#Fl
standards.all$Fl_area2 <- standards.all$Fl_area^2
Fl.poly <- lm(data=standards.all, Fl_nguL ~ Fl_area + Fl_area2)
summary(Fl.poly)
Fl.r2 <- format(summary(Fl.poly)$r.squared, digits = 3)
Fl.B0 <- summary(Fl.poly)$coefficients[1,1]
Fl.B1 <- summary(Fl.poly)$coefficients[2,1]
Fl.B2 <- summary(Fl.poly)$coefficients[3,1]
x = min(standards.all$Fl_area)
y = max(standards.all$Fl_nguL)

samples.all$Fl_nguL.uncorr <- Fl.B0 + Fl.B1*samples.all$Fl_area + Fl.B2*samples.all$Fl_area^2
ggplot(standards.all, aes(x = Fl_area, y = Fl_nguL)) +
	geom_point(data=samples.all, aes(x=Fl_area, y=Fl_nguL.uncorr, color="red", size=2))+
	geom_point() +
	xlab("Fl area")+
	ylab("Fl std concentration (ng/uL)")+
	annotate("text", x=x, y=y, hjust=-1,vjust=1,label = Fl.r2)+
	geom_smooth(method=lm, formula=y ~ poly(x, 2, raw=TRUE))+
	theme(legend.position="none")

#Pyr
standards.all$Pyr_area2 <- standards.all$Pyr_area^2
Pyr.poly <- lm(data=standards.all, Pyr_nguL ~ Pyr_area + Pyr_area2)
summary(Pyr.poly)
Pyr.r2 <- format(summary(Pyr.poly)$r.squared, digits = 3)
Pyr.B0 <- summary(Pyr.poly)$coefficients[1,1]
Pyr.B1 <- summary(Pyr.poly)$coefficients[2,1]
Pyr.B2 <- summary(Pyr.poly)$coefficients[3,1]
x = min(standards.all$Pyr_area)
y = max(standards.all$Pyr_nguL)

samples.all$Pyr_nguL.uncorr <- Pyr.B0 + Pyr.B1*samples.all$Pyr_area + Pyr.B2*samples.all$Pyr_area^2
ggplot(standards.all, aes(x = Pyr_area, y = Pyr_nguL)) +
	geom_point(data=samples.all, aes(x=Pyr_area, y=Pyr_nguL.uncorr, color="red", size=2))+
	geom_point() +
	xlab("Pyr area")+
	ylab("Pyr std concentration (ng/uL)")+
	annotate("text", x=x, y=y, hjust=-1,vjust=1,label = Pyr.r2)+
	geom_smooth(method=lm, formula=y ~ poly(x, 2, raw=TRUE))+
	theme(legend.position="none")

#BaAnt
standards.all$BaAnt_area2 <- standards.all$BaAnt_area^2
BaAnt.poly <- lm(data=standards.all, BaAnt_nguL ~ BaAnt_area + BaAnt_area2)
summary(BaAnt.poly)
BaAnt.r2 <- format(summary(BaAnt.poly)$r.squared, digits = 3)
BaAnt.B0 <- summary(BaAnt.poly)$coefficients[1,1]
BaAnt.B1 <- summary(BaAnt.poly)$coefficients[2,1]
BaAnt.B2 <- summary(BaAnt.poly)$coefficients[3,1]
x = min(standards.all$BaAnt_area)
y = max(standards.all$BaAnt_nguL)

samples.all$BaAnt_nguL.uncorr <- BaAnt.B0 + BaAnt.B1*samples.all$BaAnt_area + BaAnt.B2*samples.all$BaAnt_area^2
ggplot(standards.all, aes(x = BaAnt_area, y = BaAnt_nguL)) +
	geom_point(data=samples.all, aes(x=BaAnt_area, y=BaAnt_nguL.uncorr, color="red", size=2))+
	geom_point() +
	xlab("BaAnt area")+
	ylab("BaAnt std concentration (ng/uL)")+
	annotate("text", x=x, y=y, hjust=-1,vjust=1,label = BaAnt.r2)+
	geom_smooth(method=lm, formula=y ~ poly(x, 2, raw=TRUE))+
	theme(legend.position="none")

#Chr.Trp
standards.all$Chr.Trp_area2 <- standards.all$Chr.Trp_area^2
Chr.Trp.poly <- lm(data=standards.all, Chr.Trp_nguL ~ Chr.Trp_area + Chr.Trp_area2)
summary(Chr.Trp.poly)
Chr.Trp.r2 <- format(summary(Chr.Trp.poly)$r.squared, digits = 3)
Chr.Trp.B0 <- summary(Chr.Trp.poly)$coefficients[1,1]
Chr.Trp.B1 <- summary(Chr.Trp.poly)$coefficients[2,1]
Chr.Trp.B2 <- summary(Chr.Trp.poly)$coefficients[3,1]
x = min(standards.all$Chr.Trp_area)
y = max(standards.all$Chr.Trp_nguL)

samples.all$Chr.Trp_nguL.uncorr <- Chr.Trp.B0 + Chr.Trp.B1*samples.all$Chr.Trp_area + Chr.Trp.B2*samples.all$Chr.Trp_area^2
ggplot(standards.all, aes(x = Chr.Trp_area, y = Chr.Trp_nguL)) +
	geom_point(data=samples.all, aes(x=Chr.Trp_area, y=Chr.Trp_nguL.uncorr, color="red", size=2))+
	geom_point() +
	xlab("Chr.Trp area")+
	ylab("Chr.Trp std concentration (ng/uL)")+
	annotate("text", x=x, y=y, hjust=-1,vjust=1,label = Chr.Trp.r2)+
	geom_smooth(method=lm, formula=y ~ poly(x, 2, raw=TRUE))+
	theme(legend.position="none")

#BbjkFl
standards.all$BbjkFl_area2 <- standards.all$BbjkFl_area^2
BbjkFl.poly <- lm(data=standards.all, BbjkFl_nguL ~ BbjkFl_area + BbjkFl_area2)
summary(BbjkFl.poly)
BbjkFl.r2 <- format(summary(BbjkFl.poly)$r.squared, digits = 3)
BbjkFl.B0 <- summary(BbjkFl.poly)$coefficients[1,1]
BbjkFl.B1 <- summary(BbjkFl.poly)$coefficients[2,1]
BbjkFl.B2 <- summary(BbjkFl.poly)$coefficients[3,1]
x = min(standards.all$BbjkFl_area)
y = max(standards.all$BbjkFl_nguL)

samples.all$BbjkFl_nguL.uncorr <- BbjkFl.B0 + BbjkFl.B1*samples.all$BbjkFl_area + BbjkFl.B2*samples.all$BbjkFl_area^2
ggplot(standards.all, aes(x = BbjkFl_area, y = BbjkFl_nguL)) +
	geom_point(data=samples.all, aes(x=BbjkFl_area, y=BbjkFl_nguL.uncorr, color="red", size=2))+
	geom_point() +
	xlab("BbjkFl area")+
	ylab("BbjkFl std concentration (ng/uL)")+
	annotate("text", x=x, y=y, hjust=-1,vjust=1,label = BbjkFl.r2)+
	geom_smooth(method=lm, formula=y ~ poly(x, 2, raw=TRUE))+
	theme(legend.position="none")

#BaPyr
standards.all$BaPyr_area2 <- standards.all$BaPyr_area^2
BaPyr.poly <- lm(data=standards.all, BaPyr_nguL ~ BaPyr_area + BaPyr_area2)
summary(BaPyr.poly)
BaPyr.r2 <- format(summary(BaPyr.poly)$r.squared, digits = 3)
BaPyr.B0 <- summary(BaPyr.poly)$coefficients[1,1]
BaPyr.B1 <- summary(BaPyr.poly)$coefficients[2,1]
BaPyr.B2 <- summary(BaPyr.poly)$coefficients[3,1]
x = min(standards.all$BaPyr_area)
y = max(standards.all$BaPyr_nguL)

samples.all$BaPyr_nguL.uncorr <- BaPyr.B0 + BaPyr.B1*samples.all$BaPyr_area + BaPyr.B2*samples.all$BaPyr_area^2
ggplot(standards.all, aes(x = BaPyr_area, y = BaPyr_nguL)) +
	geom_point(data=samples.all, aes(x=BaPyr_area, y=BaPyr_nguL.uncorr, color="red", size=2))+
	geom_point() +
	xlab("BaPyr area")+
	ylab("BaPyr std concentration (ng/uL)")+
	annotate("text", x=x, y=y, hjust=-1,vjust=1,label = BaPyr.r2)+
	geom_smooth(method=lm, formula=y ~ poly(x, 2, raw=TRUE))+
	theme(legend.position="none")

#Ipyr
standards.all$Ipyr_area2 <- standards.all$Ipyr_area^2
Ipyr.poly <- lm(data=standards.all, Ipyr_nguL ~ Ipyr_area + Ipyr_area2)
summary(Ipyr.poly)
Ipyr.r2 <- format(summary(Ipyr.poly)$r.squared, digits = 3)
Ipyr.B0 <- summary(Ipyr.poly)$coefficients[1,1]
Ipyr.B1 <- summary(Ipyr.poly)$coefficients[2,1]
Ipyr.B2 <- summary(Ipyr.poly)$coefficients[3,1]
x = min(standards.all$Ipyr_area)
y = max(standards.all$Ipyr_nguL)

samples.all$Ipyr_nguL.uncorr <- Ipyr.B0 + Ipyr.B1*samples.all$Ipyr_area + Ipyr.B2*samples.all$Ipyr_area^2
ggplot(standards.all, aes(x = Ipyr_area, y = Ipyr_nguL)) +
	geom_point(data=samples.all, aes(x=Ipyr_area, y=Ipyr_nguL.uncorr, color="red", size=2))+
	geom_point() +
	xlab("Ipyr area")+
	ylab("Ipyr std concentration (ng/uL)")+
	annotate("text", x=x, y=y, hjust=-1,vjust=1,label = Ipyr.r2)+
	geom_smooth(method=lm, formula=y ~ poly(x, 2, raw=TRUE))+
	theme(legend.position="none")

#DBahAnt
standards.all$DBahAnt_area2 <- standards.all$DBahAnt_area^2
DBahAnt.poly <- lm(data=standards.all, DBahAnt_nguL ~ DBahAnt_area + DBahAnt_area2)
summary(DBahAnt.poly)
DBahAnt.r2 <- format(summary(DBahAnt.poly)$r.squared, digits = 3)
DBahAnt.B0 <- summary(DBahAnt.poly)$coefficients[1,1]
DBahAnt.B1 <- summary(DBahAnt.poly)$coefficients[2,1]
DBahAnt.B2 <- summary(DBahAnt.poly)$coefficients[3,1]
x = min(standards.all$DBahAnt_area)
y = max(standards.all$DBahAnt_nguL)

samples.all$DBahAnt_nguL.uncorr <- DBahAnt.B0 + DBahAnt.B1*samples.all$DBahAnt_area + DBahAnt.B2*samples.all$DBahAnt_area^2
ggplot(standards.all, aes(x = DBahAnt_area, y = DBahAnt_nguL)) +
	geom_point(data=samples.all, aes(x=DBahAnt_area, y=DBahAnt_nguL.uncorr, color="red", size=2))+
	geom_point() +
	xlab("DBahAnt area")+
	ylab("DBahAnt std concentration (ng/uL)")+
	annotate("text", x=x, y=y, hjust=-1,vjust=1,label = DBahAnt.r2)+
	geom_smooth(method=lm, formula=y ~ poly(x, 2, raw=TRUE))+
	theme(legend.position="none")

#BghiPer
standards.all$BghiPer_area2 <- standards.all$BghiPer_area^2
BghiPer.poly <- lm(data=standards.all, BghiPer_nguL ~ BghiPer_area + BghiPer_area2)
summary(BghiPer.poly)
BghiPer.r2 <- format(summary(BghiPer.poly)$r.squared, digits = 3)
BghiPer.B0 <- summary(BghiPer.poly)$coefficients[1,1]
BghiPer.B1 <- summary(BghiPer.poly)$coefficients[2,1]
BghiPer.B2 <- summary(BghiPer.poly)$coefficients[3,1]
x = min(standards.all$BghiPer_area)
y = max(standards.all$BghiPer_nguL)

samples.all$BghiPer_nguL.uncorr <- BghiPer.B0 + BghiPer.B1*samples.all$BghiPer_area + BghiPer.B2*samples.all$BghiPer_area^2
ggplot(standards.all, aes(x = BghiPer_area, y = BghiPer_nguL)) +
	geom_point(data=samples.all, aes(x=BghiPer_area, y=BghiPer_nguL.uncorr, color="red", size=2))+
	geom_point() +
	xlab("BghiPer area")+
	ylab("BghiPer std concentration (ng/uL)")+
	annotate("text", x=x, y=y, hjust=-1,vjust=1,label = BghiPer.r2)+
	geom_smooth(method=lm, formula=y ~ poly(x, 2, raw=TRUE))+
	theme(legend.position="none")


```



```{r}
write.csv(samples.all, "PAH_output.csv")
```

